Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-14 ms.tex
added a crosshatch models gallery

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
\caption{
Best-fit power spectra of all the NIRCam detectors.
The long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
}\label{fig:crosshatchModelGallery}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
\caption{
Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
}\label{fig:crosshatchModelGallery}
\end{figure}
